---
title: "Results Papio hormone comparison"
author: "Adrian Jaeggi"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, include=FALSE, message=FALSE, warning=FALSE)
setwd("//files.iem.uzh.ch/Data/Institute/Human_Ecology/ajaegg/Private/My Documents/Emory/Student projects/Dan Coppeto/Coppeto et al Interspecific hormone comparison")
m1<- readRDS("m1.rds")
library(brms)
library(rethinking)
post_m1<- posterior_samples(m1)
papio<- read.csv("papio.csv")

CSFOT_anubismales<- post_m1$b_logCSFOXTc_Intercept+post_m1$b_logCSFOXTc_SexM
CSFOT_hamadryasmales<- post_m1$b_logCSFOXTc_Intercept+post_m1$b_logCSFOXTc_SexM+post_m1$b_logCSFOXTc_SubspeciesHamadryas+post_m1$'b_logCSFOXTc_SubspeciesHamadryas:SexM'

CSFAVP_anubismales<- post_m1$b_logCSFAVPc_Intercept+post_m1$b_logCSFAVPc_SexM
CSFAVP_hamadryasmales<- post_m1$b_logCSFAVPc_Intercept+post_m1$b_logCSFAVPc_SexM+post_m1$b_logCSFAVPc_SubspeciesHamadryas+post_m1$'b_logCSFAVPc_SubspeciesHamadryas:SexM'

plasmaOT_anubismales<- post_m1$b_logplasmaOXTc_Intercept+post_m1$b_logplasmaOXTc_SexM
plasmaOT_hamadryasmales<- post_m1$b_logplasmaOXTc_Intercept+post_m1$b_logplasmaOXTc_SexM+post_m1$b_logplasmaOXTc_SubspeciesHamadryas+post_m1$'b_logplasmaOXTc_SubspeciesHamadryas:SexM'

urineOT_anubismales<- post_m1$b_logurineOXTc_Intercept+post_m1$b_logurineOXTc_SexM
urineOT_hamadryasmales<- post_m1$b_logurineOXTc_Intercept+post_m1$b_logurineOXTc_SexM+post_m1$b_logurineOXTc_SubspeciesHamadryas+post_m1$'b_logurineOXTc_SubspeciesHamadryas:SexM'


CSFOT_hamadryasfemales<- post_m1$b_logCSFOXTc_Intercept+post_m1$b_logCSFOXTc_SubspeciesHamadryas

CSFAVP_hamadryasfemales<- post_m1$b_logCSFAVPc_Intercept+post_m1$b_logCSFAVPc_SubspeciesHamadryas

plasmaOT_hamadryasfemales<- post_m1$b_logplasmaOXTc_Intercept+post_m1$b_logplasmaOXTc_SubspeciesHamadryas

urineOT_hamadryasfemales<- post_m1$b_logurineOXTc_Intercept+post_m1$b_logurineOXTc_SubspeciesHamadryas

```

## Results

We found no consistent support for species differences in hormone levels (Figure 1). Adjusting for covariates (see Table S1), hamadryas females did not have consistently higher hormone levels than anubis females (CSF OT: median difference=`r round(median(post_m1$b_logCSFOXTc_SubspeciesHamadryas),2)`, 90% CI=`r round(HPDI(post_m1$b_logCSFOXTc_SubspeciesHamadryas, prob=0.9)[1],2)` - `r round(HPDI(post_m1$b_logCSFOXTc_SubspeciesHamadryas, prob=0.9)[2],2)`, PP~hamadryas>anubis~=`r round(sum(post_m1$b_logCSFOXTc_SubspeciesHamadryas>0)/length(post_m1$b_logCSFOXTc_SubspeciesHamadryas),2)`; plasma OT: median difference=`r round(median(post_m1$b_logplasmaOXTc_SubspeciesHamadryas),2)`, 90% CI=`r round(HPDI(post_m1$b_logplasmaOXTc_SubspeciesHamadryas, prob=0.9)[1],2)` - `r round(HPDI(post_m1$b_logplasmaOXTc_SubspeciesHamadryas, prob=0.9)[2],2)`, PP~hamadryas>anubis~=`r round(sum(post_m1$b_logplasmaOXTc_SubspeciesHamadryas>0)/length(post_m1$b_logplasmaOXTc_SubspeciesHamadryas),2)`; urinary OT: median difference=`r round(median(post_m1$b_logurineOXTc_SubspeciesHamadryas),2)`, 90% CI=`r round(HPDI(post_m1$b_logurineOXTc_SubspeciesHamadryas, prob=0.9)[1],2)` - `r round(HPDI(post_m1$b_logurineOXTc_SubspeciesHamadryas, prob=0.9)[2],2)`, PP~hamadryas>anubis~=`r round(sum(post_m1$b_logurineOXTc_SubspeciesHamadryas>0)/length(post_m1$b_logurineOXTc_SubspeciesHamadryas),2)`; CSF AVP: median difference=`r round(median(post_m1$b_logCSFAVPc_SubspeciesHamadryas),2)`, 90% CI=`r round(HPDI(post_m1$b_logCSFAVPc_SubspeciesHamadryas, prob=0.9)[1],2)` - `r round(HPDI(post_m1$b_logCSFAVPc_SubspeciesHamadryas, prob=0.9)[2],2)`, PP~hamadryas>anubis~=`r round(sum(post_m1$b_logCSFAVPc_SubspeciesHamadryas>0)/length(post_m1$b_logCSFAVPc_SubspeciesHamadryas),2)`), nor did hamadryas males have consistently higher levels than anubis males (CSF OT: median difference=`r round(median(CSFOT_hamadryasmales-CSFOT_anubismales),2)`, 90% CI=`r round(HPDI(CSFOT_hamadryasmales-CSFOT_anubismales, prob=0.9)[1],2)` - `r round(HPDI(CSFOT_hamadryasmales-CSFOT_anubismales, prob=0.9)[2],2)`, PP~hamadryas>anubis~=`r round(sum(CSFOT_hamadryasmales-CSFOT_anubismales>0)/length(CSFOT_hamadryasmales),2)`; Plasma OT: median difference=`r round(median(plasmaOT_hamadryasmales-plasmaOT_anubismales),2)`, 90% CI=`r round(HPDI(plasmaOT_hamadryasmales-plasmaOT_anubismales, prob=0.9)[1],2)` - `r round(HPDI(plasmaOT_hamadryasmales-plasmaOT_anubismales, prob=0.9)[2],2)`, PP~hamadryas>anubis~=`r round(sum(plasmaOT_hamadryasmales-plasmaOT_anubismales>0)/length(plasmaOT_hamadryasmales),2)`; Urinary OT: median difference=`r round(median(urineOT_hamadryasmales-urineOT_anubismales),2)`, 90% CI=`r round(HPDI(urineOT_hamadryasmales-urineOT_anubismales, prob=0.9)[1],2)` - `r round(HPDI(urineOT_hamadryasmales-urineOT_anubismales, prob=0.9)[2],2)`, PP~hamadryas>anubis~=`r round(sum(urineOT_hamadryasmales-urineOT_anubismales>0)/length(urineOT_hamadryasmales),2)`; CSF AVP: median difference=`r round(median(CSFAVP_hamadryasmales-CSFAVP_anubismales),2)`, 90% CI=`r round(HPDI(CSFAVP_hamadryasmales-CSFAVP_anubismales, prob=0.9)[1],2)` - `r round(HPDI(CSFAVP_hamadryasmales-CSFAVP_anubismales, prob=0.9)[2],2)`, PP~hamadryas>anubis~=`r round(sum(CSFAVP_hamadryasmales-CSFAVP_anubismales>0)/length(CSFAVP_hamadryasmales),2)`). These results did not change qualitatively when analyzing each hormone separately (see Supplementary Results).

Other associations provide important biological validation. Consistent with OT's reproductive functions, anubis females had higher OT levels than males (CSF OT: median difference=`r -round(median(post_m1$b_logCSFOXTc_SexM),2)`, 90% CI=`r -round(HPDI(post_m1$b_logCSFOXTc_SexM, prob=0.9)[1],2)` - `r -round(HPDI(post_m1$b_logCSFOXTc_SexM, prob=0.9)[2],2)`, PP~females>males~=`r round(sum(post_m1$b_logCSFOXTc_SexM<0)/length(post_m1$b_logCSFOXTc_SexM),2)`; Plasma OT: median difference=`r -round(median(post_m1$b_logplasmaOXTc_SexM),2)`, 90% CI=`r -round(HPDI(post_m1$b_logplasmaOXTc_SexM, prob=0.9)[1],2)` - `r -round(HPDI(post_m1$b_logplasmaOXTc_SexM, prob=0.9)[2],2)`, PP~females>males~=`r round(sum(post_m1$b_logplasmaOXTc_SexM<0)/length(post_m1$b_logplasmaOXTc_SexM),2)`; Urinary OT: median difference=`r -round(median(post_m1$b_logurineOXTc_SexM),2)`, 90% CI=`r -round(HPDI(post_m1$b_logurineOXTc_SexM, prob=0.9)[1],2)` - `r -round(HPDI(post_m1$b_logurineOXTc_SexM, prob=0.9)[2],2)`, PP~females>males~=`r round(sum(post_m1$b_logurineOXTc_SexM<0)/length(post_m1$b_logurineOXTc_SexM),2)`). While this sex difference was less pronounced for non-pregnant hamadryas (CSF OT: median difference=`r round(median(CSFOT_hamadryasfemales-CSFOT_hamadryasmales),2)`, 90% CI=`r round(HPDI(CSFOT_hamadryasfemales-CSFOT_hamadryasmales, prob=0.9)[1],2)` - `r round(HPDI(CSFOT_hamadryasfemales-CSFOT_hamadryasmales, prob=0.9)[2],2)`, PP~females>males~=`r round(sum(CSFOT_hamadryasfemales-CSFOT_hamadryasmales>0)/length(CSFOT_hamadryasfemales),2)`; Plasma OT: median difference=`r round(median(plasmaOT_hamadryasfemales-plasmaOT_hamadryasmales),2)`, 90% CI=`r round(HPDI(plasmaOT_hamadryasfemales-plasmaOT_hamadryasmales, prob=0.9)[1],2)` - `r round(HPDI(plasmaOT_hamadryasfemales-plasmaOT_hamadryasmales, prob=0.9)[2],2)`, PP~females>males~=`r round(sum(plasmaOT_hamadryasfemales-plasmaOT_hamadryasmales>0)/length(plasmaOT_hamadryasfemales),2)`; Urinary OT: median difference=`r round(median(urineOT_hamadryasfemales-urineOT_hamadryasmales),2)`, 90% CI=`r round(HPDI(urineOT_hamadryasfemales-urineOT_hamadryasmales, prob=0.9)[1],2)` - `r round(HPDI(urineOT_hamadryasfemales-urineOT_hamadryasmales, prob=0.9)[2],2)`, PP~females>males~=`r round(sum(urineOT_hamadryasfemales-urineOT_hamadryasmales>0)/length(urineOT_hamadryasfemales),2)`),  peripheral OT levels were positively associated with gestational day (Plasma OT: median slope=`r round(median(post_m1$b_logplasmaOXTc_GD_DOC),2)`, 90% CI=`r round(HPDI(post_m1$b_logplasmaOXTc_GD_DOC, prob=0.9)[1],2)` - `r round(HPDI(post_m1$b_logplasmaOXTc_GD_DOC, prob=0.9)[2],2)`, PP~slope>0~=`r round(sum(post_m1$b_logplasmaOXTc_GD_DOC>0)/length(post_m1$b_logplasmaOXTc_GD_DOC),2)`; Urinary OT: median slope=`r round(median(post_m1$b_logurineOXTc_GD_DOC),2)`, 90% CI=`r round(HPDI(post_m1$b_logurineOXTc_GD_DOC, prob=0.9)[1],2)` - `r round(HPDI(post_m1$b_logurineOXTc_GD_DOC, prob=0.9)[2],2)`, PP~slope>0~=`r round(sum(post_m1$b_logurineOXTc_GD_DOC>0)/length(post_m1$b_logurineOXTc_GD_DOC),2)`). Other covariates (age, weight, lactation status, corral size) did not consistently associate with hormone levels, and variation between corrals tended to be smaller than variation within corrals (for full details see Tables S1 & S2). 

Finally, residual correlations among OT levels from different sources were negligible (CSF OT ~ Plasma OT: median r=`r round(median(post_m1$rescor__logCSFOXTc__logplasmaOXTc),2)`, 90% CI=`r round(HPDI(post_m1$rescor__logCSFOXTc__logplasmaOXTc, prob=0.9)[1],2)` - `r round(HPDI(post_m1$rescor__logCSFOXTc__logplasmaOXTc, prob=0.9)[2],2)`, PP~r>0~=`r round(sum(post_m1$rescor__logCSFOXTc__logplasmaOXTc>0)/length(post_m1$rescor__logCSFOXTc__logplasmaOXTc),2)`; Plasma OT ~ Urinary OT: median r=`r round(median(post_m1$rescor__logplasmaOXTc__logurineOXTc),2)`, 90% CI=`r round(HPDI(post_m1$rescor__logplasmaOXTc__logurineOXTc, prob=0.9)[1],2)` - `r round(HPDI(post_m1$rescor__logplasmaOXTc__logurineOXTc, prob=0.9)[2],2)`, PP~r>0~=`r round(sum(post_m1$rescor__logplasmaOXTc__logurineOXTc>0)/length(post_m1$rescor__logplasmaOXTc__logurineOXTc),2)`), except for a _negative_ correlation between CSF and urinary OT (median r=`r round(median(post_m1$rescor__logCSFOXTc__logurineOXTc),2)`, 90% CI=`r round(HPDI(post_m1$rescor__logCSFOXTc__logurineOXTc, prob=0.9)[1],2)` - `r round(HPDI(post_m1$rescor__logCSFOXTc__logurineOXTc, prob=0.9)[2],2)`, PP~r<0~=`r round(sum(post_m1$rescor__logCSFOXTc__logurineOXTc<0)/length(post_m1$rescor__logCSFOXTc__logurineOXTc),2)`). CSF AVP levels were weakly positively correlated with CSF OT and negatively with urinary OT (CSF AVP ~ CSF OT: median r=`r round(median(post_m1$rescor__logCSFOXTc__logCSFAVPc),2)`, 90% CI=`r round(HPDI(post_m1$rescor__logCSFOXTc__logCSFAVPc, prob=0.9)[1],2)` - `r round(HPDI(post_m1$rescor__logCSFOXTc__logCSFAVPc, prob=0.9)[2],2)`, PP~r>0~=`r round(sum(post_m1$rescor__logCSFOXTc__logCSFAVPc>0)/length(post_m1$rescor__logCSFOXTc__logCSFAVPc),2)`; CSF AVP ~ Plasma OT: median r=`r round(median(post_m1$rescor__logplasmaOXTc__logCSFAVPc),2)`, 90% CI=`r round(HPDI(post_m1$rescor__logplasmaOXTc__logCSFAVPc, prob=0.9)[1],2)` - `r round(HPDI(post_m1$rescor__logplasmaOXTc__logCSFAVPc, prob=0.9)[2],2)`, PP~r>0~=`r round(sum(post_m1$rescor__logplasmaOXTc__logCSFAVPc>0)/length(post_m1$rescor__logplasmaOXTc__logCSFAVPc),2)`; CSF AVP ~ Urinary OT: median r=`r round(median(post_m1$rescor__logurineOXTc__logCSFAVPc),2)`, 90% CI=`r round(HPDI(post_m1$rescor__logurineOXTc__logCSFAVPc, prob=0.9)[1],2)` - `r round(HPDI(post_m1$rescor__logurineOXTc__logCSFAVPc, prob=0.9)[2],2)`, PP~r>0~=`r round(sum(post_m1$rescor__logurineOXTc__logCSFAVPc>0)/length(post_m1$rescor__logurineOXTc__logCSFAVPc),2)`).


```{r Figure 1}
library(MetBrewer)
col.ham.female<- MetPalettes$Lakota[[1]][1]
col.ham.male<- MetPalettes$Lakota[[1]][2]
col.an.female<- MetPalettes$Lakota[[1]][6]
col.an.male<- MetPalettes$Lakota[[1]][3]

tiff("Figure 1.tif", compression="lzw", height=6.0, width=12.0, units="cm", res=600, pointsize=5)

par(mfrow=c(2,4), oma=c(3,3,0,0), mar=c(3,2,3,1))

dens(post_m1$b_logCSFOXTc_SubspeciesHamadryas, xlab="", ylab="", main="", col="white", ylim=c(0,1.5), xlim=c(-1,2), bty = "n")
polygon(density(post_m1$b_logCSFOXTc_Intercept+post_m1$b_logCSFOXTc_SubspeciesHamadryas), col=adjustcolor(col.ham.female, alpha.f=0.5))
polygon(density(post_m1$b_logCSFOXTc_Intercept), col=adjustcolor(col.an.female, alpha.f=0.5))
polygon(density(post_m1$b_logCSFOXTc_SubspeciesHamadryas), col=NULL, lty=2)
abline(v=0)
legend("topright", legend=round(sum(post_m1$b_logCSFOXTc_SubspeciesHamadryas>0)/length(post_m1$b_logCSFOXTc_SubspeciesHamadryas),2), border="white", bty="n", cex=1.2, inset=0.1)

mtext(text="Probability Density",side=2,line=1,outer=TRUE)
mtext(text="CSF Oxytocin",side=3,line=1)

dens(post_m1$b_logplasmaOXTc_SubspeciesHamadryas, xlab="", ylab="", main="", col="white", ylim=c(0,1.2), xlim=c(-2,1.5), bty = "n")
polygon(density(post_m1$b_logplasmaOXTc_Intercept+post_m1$b_logplasmaOXTc_SubspeciesHamadryas), col=adjustcolor(col.ham.female, alpha.f=0.5))
polygon(density(post_m1$b_logplasmaOXTc_Intercept), col=adjustcolor(col.an.female, alpha.f=0.5))
polygon(density(post_m1$b_logplasmaOXTc_SubspeciesHamadryas), col=NULL, lty=2)
abline(v=0)
mtext(text="Plasma Oxytocin",side=3,line=1)
legend("topright", legend=round(sum(post_m1$b_logplasmaOXTc_SubspeciesHamadryas>0)/length(post_m1$b_logplasmaOXTc_SubspeciesHamadryas),2), border="white", bty="n", cex=1.2, inset=0.1)

dens(post_m1$b_logurineOXTc_SubspeciesHamadryas, xlab="", ylab="", main="", col="white", ylim=c(0,1.5), xlim=c(-2,1.5), bty = "n")
polygon(density(post_m1$b_logurineOXTc_Intercept+post_m1$b_logurineOXTc_SubspeciesHamadryas), col=adjustcolor(col.ham.female, alpha.f=0.5))
polygon(density(post_m1$b_logurineOXTc_Intercept), col=adjustcolor(col.an.female, alpha.f=0.5))
polygon(density(post_m1$b_logurineOXTc_SubspeciesHamadryas), col=NULL, lty=2)
abline(v=0)
mtext(text="Urinary Oxytocin",side=3,line=1)
legend("topright", legend=round(sum(post_m1$b_logurineOXTc_SubspeciesHamadryas>0)/length(post_m1$b_logurineOXTc_SubspeciesHamadryas),2), border="white", bty="n", cex=1.2, inset=0.1)

dens(post_m1$b_logCSFAVPc_SubspeciesHamadryas, xlab="", ylab="", main="", col="white", ylim=c(0,1.6), xlim=c(-1.5,1.5), bty = "n")
polygon(density(post_m1$b_logCSFAVPc_Intercept+post_m1$b_logCSFAVPc_SubspeciesHamadryas), col=adjustcolor(col.ham.female, alpha.f=0.5))
polygon(density(post_m1$b_logCSFAVPc_Intercept), col=adjustcolor(col.an.female, alpha.f=0.5))
polygon(density(post_m1$b_logCSFAVPc_SubspeciesHamadryas), col=NULL, lty=2)
abline(v=0)
mtext("Females",cex=1, side=4,line=0, las = 0)
mtext(text="CSF Arginine Vasopressin",side=3,line=1)
legend("topright", legend=round(sum(post_m1$b_logCSFAVPc_SubspeciesHamadryas>0)/length(post_m1$b_logCSFAVPc_SubspeciesHamadryas),2), border="white", bty="n", cex=1.2, inset=0.1)

par(mar=c(2,2,4,1))

dens(CSFOT_hamadryasmales, xlab="", ylab="", main="", col="white", ylim=c(0,1.5), xlim=c(-1.5,2.5), bty = "n")
polygon(density(CSFOT_hamadryasmales), col=adjustcolor(col.ham.male, alpha.f=0.5))
polygon(density(CSFOT_anubismales), col=adjustcolor(col.an.male, alpha.f=0.5))
polygon(density(CSFOT_hamadryasmales-CSFOT_anubismales), col=NULL, lty=2)
abline(v=0)
legend("topright", legend=round(sum(CSFOT_hamadryasmales-CSFOT_anubismales>0)/length(CSFOT_hamadryasmales),2), border="white", bty="n", cex=1.2, inset=0.1)

dens(plasmaOT_hamadryasmales, xlab="", ylab="", main="", col="white", ylim=c(0,1.2), xlim=c(-3,1.5), bty = "n")
polygon(density(plasmaOT_hamadryasmales), col=adjustcolor(col.ham.male, alpha.f=0.5))
polygon(density(plasmaOT_anubismales), col=adjustcolor(col.an.male, alpha.f=0.5))
polygon(density(plasmaOT_hamadryasmales-plasmaOT_anubismales), col=NULL, lty=2)
abline(v=0)
legend("topright", legend=round(sum(plasmaOT_hamadryasmales-plasmaOT_anubismales>0)/length(plasmaOT_hamadryasmales),2), border="white", bty="n", cex=1.2, inset=0.1)

dens(urineOT_hamadryasmales, xlab="", ylab="", main="", col="white", ylim=c(0,1.3), xlim=c(-3,1), bty = "n")
polygon(density(urineOT_hamadryasmales), col=adjustcolor(col.ham.male, alpha.f=0.5))
polygon(density(urineOT_anubismales), col=adjustcolor(col.an.male, alpha.f=0.5))
polygon(density(urineOT_hamadryasmales-urineOT_anubismales), col=NULL, lty=2)
abline(v=0)
legend("topright", legend=round(sum(urineOT_hamadryasmales-urineOT_anubismales>0)/length(urineOT_hamadryasmales),2), border="white", bty="n", cex=1.2, inset=0.1)

dens(CSFAVP_hamadryasmales, xlab="", ylab="", main="", col="white", ylim=c(0,1.5), bty = "n")
polygon(density(CSFAVP_hamadryasmales), col=adjustcolor(col.ham.male, alpha.f=0.5))
polygon(density(CSFAVP_anubismales), col=adjustcolor(col.an.male, alpha.f=0.5))
polygon(density(CSFAVP_hamadryasmales-CSFAVP_anubismales), col=NULL, lty=2)
abline(v=0)
mtext("Males",cex=1, side=4,line=0, las = 0)
legend("topright", legend=round(sum(CSFAVP_hamadryasmales-CSFAVP_anubismales>0)/length(CSFAVP_hamadryasmales),2), border="white", bty="n", cex=1.2, inset=0.1)

mtext("log hormone levels [centered]",cex=1, side=1,line=1, outer=TRUE)

# add legend in the center
par(xpd=NA)

legend(x=-20, y=2.2, ncol=2, fill=c(adjustcolor(col.ham.female, alpha.f=0.5),adjustcolor(col.an.female, alpha.f=0.5),adjustcolor(col.ham.male, alpha.f=0.5),adjustcolor(col.an.male, alpha.f=0.5)), border="black", legend=c("Hamadryas Females", "Anubis Females", "Hamadryas Males", "Anubis Males"), bty="n", cex=1.8, pt.cex=1.8)

legend(x=-8, y=2.1, lty=2, seg.len=2, legend="Hamadryas - Anubis", bty="n", cex=1.8, pt.cex=1.8)

dev.off()

```